Exoplanet population inference and the abundance \\ of Earth analogs from noisy, incomplete catalogs

### 2014-08-31 document/ms.tex
updating results DOI
adding comparison figure and changing labels (#19)

\newcommand{\resultsurl}{\url{http://dx.doi.org/10.6084/m9.figshare.1051864}}

@@

\dfmtodo{Add a few more pedagogical words here.}

@@

Although they are mainly nuisance parameters, we also obtain posterior
constraints on the hyperparameters \mean\ and \smoothpars.
In particular, the constraints on the length scales in $\ln \period$ and $\ln
\radius$ are $\smooth_\period = 3.65 \pm 1.03$ and $\smooth_\radius = 0.65 \pm
0.12$ respectively.
Both of these scales are larger than a bin in their respective dimension.
For completeness we also find the following constraints on the other
hyperparameters
\begin{eqnarray}
\mean = 5.44 \pm 1.56 &\quad& \ln\smooth_0 = 1.68 \pm 0.72 \quad.
\end{eqnarray}
The MCMC chains used to compute these values is available
online\footnote{\resultsurl}.

@@

To examine the effects of measurement uncertainties, we repeat our analysis
with the error bars on the radii artificially set to zero, keeping everything
else the same.
This analysis (labeled ``negligible uncertainties'' in \fig{comparison}) gives
the result
\begin{eqnarray}
\Gamma_\oplus &=& 0.040^{+0.031}_{-0.019} \quad.
\end{eqnarray}
This result is relatively more precise and higher than our final result and
consistent with the value obtained with linear extrapolation.
This confirms the hypothesis that the discrepancy between our result and the
previously published values is the combined result of both of our key
generalizations.

@@

\begin{figure}[p]
\begin{center}
\includegraphics[width=\textwidth]{figures/comparison.pdf}
\end{center}
\caption{%
Comparison of various estimates of \gammaearth.
From the top, the first value is the number published by \citet{petigura} and
converted to consistent units.
The second point shows the value implied by the power law model for the
occurrence rate of $1-2\,R_\oplus$ planets from \citet{dong}.
The point labeled ``linear extrapolation'' is the result of modeling the
distribution of small planets ($1-2\,R_\oplus$) on long periods
($50-400\,\mathrm{days}$) but allowing the period distribution to be
\emph{linear} instead of \emph{uniform}.
The ``negligible uncertainties'' value is given by applying the model
developed in this \paper\ but with the error bars on radius artificially
set to zero.
Finally, the bottom point is the result of our full analysis.
\figlabel{comparison}}
\end{figure}

>>>>

\newcommand{\resultsurl}{\url{http://dx.doi.org/10.5281/zenodo.11507}}

@@

@@

Although they are mainly nuisance parameters, we also obtain posterior
constraints on the hyperparameters \mean\ and \smoothpars.
In particular, the constraints on the length scales in $\ln \period$ and $\ln
\radius$ are $\smooth_\period = 3.65 \pm 1.03$ and $\smooth_\radius = 0.65 \pm
0.12$ respectively.
Both of these scales are larger than a bin in their respective dimension.
For completeness we also find the following constraints on the other
hyperparameters
\begin{eqnarray}
\mean = 5.44 \pm 1.56 &\quad\mathrm{and}\quad&
\ln\smooth_0 = 1.68 \pm 0.72 \quad.
\end{eqnarray}
The MCMC chains used to compute these values is available
online\footnote{\resultsurl}.

@@

To examine the effects of measurement uncertainties, we repeat our analysis
with the error bars on the radii artificially set to zero, keeping everything
else the same.
This analysis (labeled ``uncertainties ignored'' in \fig{comparison}) gives
the result
\begin{eqnarray}
\Gamma_\oplus &=& 0.040^{+0.031}_{-0.019} \quad.
\end{eqnarray}
This result is relatively more precise and higher than our final result and
consistent with the value obtained with linear extrapolation.
This confirms the hypothesis that the discrepancy between our result and the
previously published values is the combined result of both of our key
generalizations.

@@

\begin{figure}[p]
\begin{center}
\includegraphics[width=\textwidth]{figures/comparison.pdf}
\end{center}
\caption{%
Comparison of various estimates of \gammaearth.
From the top, the first value is the number published by \citet{petigura} and
converted to consistent units.
The second point shows the value implied by the power law model for the
occurrence rate of $1-2\,R_\oplus$ planets from \citet{dong}.
The point labeled ``linear extrapolation'' is the result of modeling the
distribution of small planets ($1-2\,R_\oplus$) on long periods
($50-400\,\mathrm{days}$) but allowing the period distribution to be
\emph{linear} instead of \emph{uniform}.
The ``uncertainties ignored'' value is given by applying the model
developed in this \paper\ but with the error bars on radius artificially
set to zero.
Finally, the bottom point is the result of our full analysis.
\figlabel{comparison}}
\end{figure}
